Formation of $\cenn$ Molecules in Oxygen-rich Interiors of Type II Supernovae

### 2013-01-30 doc/submit/ms.tex
Fix typoes.

Figure \ref{fig:ncoc2} displays the number density $n_{\ctwo}$ along with
that of $n_{CO}$.
Our examination of flows into $\ctwo$\ shows that the reaction
\coctoctwo\ competes with the reaction \twoctoctwo\ only in the
range 3400 K $< T < 3900$ K, but falls steeply for greater or lesser
temperature.  At higher $T$ the abundance of CO is too small to create
$\ctwo$\ in this way, and at smaller $T$ the cross section for \coctoctwo\
declines too precipitously.  \citet{2009ApJ...703..642C} missed that
because their calculated abundance of CO was much too large.
At its maximum $n_{\ctwo} =0.1$ cm$^{-3}$ is only about
$10^{-7}$ of $n_{CO}$. The reason $\ctwo$\ is so rare is that its dissociation
rate by thermal photons is much faster than that for CO because the binding
energy of $\ctwo$\ is
so much less than that for CO.
The smaller value of $\tau_\gamma$ causes the steady stat with thermal
radiation for $\ctwo$, as in Eq. (\ref{eq:dycodt}), to be much smaller that for
CO, so $n_{\ctwo}$ grows much more slowly than $n_{CO}$.  The Compton
electron lifetime $\tau_e$ never plays a role for $\ctwo$, but the
lifetime against oxidation becomes faster that $\tau_\gamma$ when $T$
falls below 3500 K.  That transition establishes the maximum in
Fig. \ref{fig:ncoc2}.
This $n_{\ctwo}$
maximum differs greatly
from results in \citet{2009ApJ...703..642C}, where their Fig. 11 shows the
maximum atom fraction of $n_{\ctwo}$ to be near $10^{-5}$,
equal to about $10^5$ cm$^{-3}$, almost 1\% of their $n_{CO}$ at that time.
And their maximum for $\ctwo$\ occurs near 7000 K, far too hot for $\ctwo$\ to
be abundant in the face of rapid photodissociation. The huge differences between
these two computations require an explanation. We find it likely that
\cite{2009ApJ...703..642C} inadvertently omitted photodissociation by thermal
photons from their destruction rates.

@@

One sees from Fig. \ref{fig:cn} that the \coctoctwo\ reaction plays no
role in $\ceightr$\ production from the fact that $\ceightr$\ rises only for
$t - t(6000 {\rm K}) > 1.5 \times 10^7$ s, corresponding to $T < 2000$ K,
despite $\ctwo$\ and $\cthree$\ rising at much earlier times.
Whatsoever $\ctwo$\ is made earlier plays no role in $\ceightr$\ production
because there ejection of C atoms from $\cenn$\ at higher $T$ prevents the
flow to $\ceight$.  Only at $T < 2000$ K do those photodissociation reactions
become so slow that $\ceight$\ can grow, which it does from the $\ctwo$\
recently
formed by the \twoctoctwo\ reaction near 2000 K.  Fig. \ref{fig:cn} also shows
that $Y(\ceightr)$
grows quickly to $10^{-16}$.  Since available C is $Y_C = 0.1$,
the ratio gives $10^{-15}$ C/ring.  This is enough to grow very large
graphite.

>>>>

Figure \ref{fig:ncoc2} displays the number density $n_{\ctwo}$ along with
that of $n_{CO}$.
Our examination of flows into $\ctwo$\ shows that the reaction
\coctoctwo\ competes with the reaction \twoctoctwo\ only in the
range 3400 K $< T < 3900$ K, but falls steeply for greater or lesser
temperature.  At higher $T$ the abundance of CO is too small to create
$\ctwo$\ in this way, and at smaller $T$ the cross section for \coctoctwo\
declines too precipitously.  \citet{2009ApJ...703..642C} missed that
because their calculated abundance of CO was much too large.
At its maximum $n_{\ctwo} =0.1$ cm$^{-3}$ is only about
$10^{-7}$ of $n_{CO}$. The reason $\ctwo$\ is so rare is that its dissociation
rate by thermal photons is much faster than that for CO because the binding
energy of $\ctwo$\ is
so much less than that for CO.
The smaller value of $\tau_\gamma$ causes the steady state with thermal
radiation for $\ctwo$, as in Eq. (\ref{eq:dycodt}), to be much smaller than 
that for CO, so $n_{\ctwo}$ grows much more slowly than $n_{CO}$.  The Compton
electron lifetime $\tau_e$ never plays a role for $\ctwo$, but the
lifetime against oxidation becomes faster that $\tau_\gamma$ when $T$
falls below 3500 K.  That transition establishes the maximum in
Fig. \ref{fig:ncoc2}.
This $n_{\ctwo}$
maximum differs greatly
from results in \citet{2009ApJ...703..642C}, where their Fig. 11 shows the
maximum atom fraction of $n_{\ctwo}$ to be near $10^{-5}$,
equal to about $10^5$ cm$^{-3}$, almost 1\% of their $n_{CO}$ at that time.
And their maximum for $\ctwo$\ occurs near 7000 K, far too hot for $\ctwo$\ to
be abundant in the face of rapid photodissociation. The huge differences between
these two computations require an explanation. We find it likely that
\cite{2009ApJ...703..642C} inadvertently omitted photodissociation by thermal
photons from their destruction rates.

@@

One sees from Fig. \ref{fig:Yi} that the \coctoctwo\ reaction plays no
role in $\ceightr$\ production from the fact that $\ceightr$\ rises only for
$t - t(6000 {\rm K}) > 1.5 \times 10^7$ s, corresponding to $T < 2000$ K,
despite $\ctwo$\ and $\cthree$\ rising at much earlier times.
Whatsoever $\ctwo$\ is made earlier plays no role in $\ceightr$\ production
because there ejection of C atoms from $\cenn$\ at higher $T$ prevents the
flow to $\ceight$.  Only at $T < 2000$ K do those photodissociation reactions
become so slow that $\ceight$\ can grow, which it does from the $\ctwo$\
recently
formed by the \twoctoctwo\ reaction near 2000 K.  Fig. \ref{fig:Yi} also shows
that $Y(\ceightr)$
grows quickly to $10^{-16}$.  Since available C is $Y_C = 0.1$,
the ratio gives $10^{-15}$ C/ring.  This is enough to grow very large
graphite.
